Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-10 WRITEUP/ms.tex

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating global quantities for MCS, we always perform a mass-weighting. Since we operate on data on a unigrid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the defintion \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right)^2 \right\rangle\,,
\end{equation}
where the pressure is in units of [K\,\cc], $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, the contribution from the non-thermal energy is calculated from the non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n} \right)^2 \right\rangle\,.
\end{equation}
%
It is also convenient to write the Mach number
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}
\AP{in the following two paragraphs we are mixing results and expectations. The might be moved to th result section}
As the non-thermal pressure contribution dominates the thermal one for dense gas \citet{Pallottini17b}, the local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds $\mathcal{M} \sim 10$ for \flower.
%
Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to showw the point?}, but this depends on the evolutionary stage of \flower.
%
%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.

>>>>

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating global quantities for MCS, we always perform a mass-weighting. Since we operate on data on a unigrid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the defintion \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \frac{\sum_{i} \rho_i \left(P_{{\rm TH}, i}~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
c_s^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right)^2 \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n} \right)^2 \right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

\subsection{Distributions of MCC Basic Properties}

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
 In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
%
Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to show the point?}\DL{This is currently shown in \Fig{vv}}, but this depends on the evolutionary stage of \flower.
%
%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.
